Testing atlantisom: true biomass output from Atlantis

### 2019-04-29 TrueBioTest.Rmd
fix error in filter, change alpha level

atBtxt2tidy <- atBtxt2 %>%
  select(Time:DIN) %>%
  #select(Time, FPL:DIN) %>%
  rename_(.dots=with(groupslookup, setNames(as.list(as.character(Code)), Name))) %>%
  gather(species, biomass, -Time) %>%
  filter(species == levels(surveyB_frombio$species))

#all species comparison, time intervals hardcoded for NEUS and NOBA
compareB <-ggplot() +
  geom_line(data=surveyB_frombio, aes(x=time/5,y=atoutput, color="survey census B"), 
            alpha = 3/10) +
  geom_point(data=atBtxt2tidy, aes(x=Time/365,y=biomass, color="txt output true B"),
             alpha = 3/10) + 
  theme_tufte() +
  theme(legend.position = "top") +
  labs(colour=scenario.name)

>>>>

atBtxt2tidy <- atBtxt2 %>%
  select(Time:DIN) %>%
  #select(Time, FPL:DIN) %>%
  rename_(.dots=with(groupslookup, setNames(as.list(as.character(Code)), Name))) %>%
  gather(species, biomass, -Time) %>%
  filter(species %in% levels(surveyB_frombio$species))

#all species comparison, time intervals hardcoded for NEUS and NOBA
compareB <-ggplot() +
  geom_line(data=surveyB_frombio, aes(x=time/5,y=atoutput, color="survey census B"), 
            alpha = 10/10) +
  geom_point(data=atBtxt2tidy, aes(x=Time/365,y=biomass, color="txt output true B"),
             alpha = 1/10) + 
  theme_tufte() +
  theme(legend.position = "top") +
  labs(colour=scenario.name)
